\subsection*{Abstract}
%System designers and developers want users to be able to 
%run applications -- even untrusted ones -- on open source operating systems 
%without triggering potential security breaches. Yet, a possible compromise of privileged code 
%in the OS kernel is particularly dangerous because bugs or flaws triggered there pose a direct security threat 
%to the system itself and all other programs running in it. 

Running untrusted programs on a vulnerable operating system kernel is a big challenge. 
%A number of security strategies have evolved over the years in response to these concerns, 
A number of security strategies have evolved over the years, trying to solve this problem, 
such as system call interposition, operating system virtual machines, and library OSes. 
However, without a widely applicable quantitative metric to guide efforts, systems for securing privileged code 
have emerged on almost a ``case-by-case'' basis. To develop more consistently effective security systems, 
more needs to be known about the location of flaws in kernel code.

In this paper, we document the development, testing, and application of a new design for a secure virtual machine 
that is based on a more accurate determination of which lines of code can be executed safely within the Linux OS kernel. 
With this knowledge, we devise a security metric called \emph{Lock-in-Pop}, as it locks out application access to all kernel code 
except that found in paths associated with frequently-used popular programs and is shown to contain fewer vulnerabilities. 
Using this new design scheme, we build and test  a secure virtual machine called Lind that accesses only 
the popular code paths through a very small trusted computing base. Complex functionality is addressed 
by using a memory-safe programming language to recreate riskier system calls within a sandbox. 
Our test results for 35 bugs examined in Linux kernel version 3.14.1, show that Lind can reduce the threat of an attack to less than 3\%. 
This result is about an order of magnitude better than existing systems like VirtualBox (40\%), VMWare Workstation (31\%), Docker (23\%), 
LXC (34\%), QEMU (14\%), KVM (14\%), and Graphene (23\%).